### 2019-09-06 README.Rmd
Update README

@@

This repository contains all code and text associated with the publication (in french):

@@

This repository is organized as an R package. You can download the compendium as a zip from from this [URL](https://github.com/nfrerebeau/archeosciences2019/releases).

@@

* The Rmarkdown source file of the manuscript,
* All the figures generated from R code (in the `figures/` subdirectory),
* All the raw data files (in CSV format, in the `data/` subdirectory),
* Code files used for data cleaning (in the `scripts/` subdirectory).

>>>>

[![Travis-CI Build Status](https://travis-ci.org/nfrerebeau/archeosciences2019.svg?branch=master)](https://travis-ci.org/nfrerebeau/archeosciences2019)
[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/nfrerebeau/archeosciences2019/master?urlpath=rstudio)

@@

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2613512.svg)](https://doi.org/10.5281/zenodo.2613512)

This repository contains the data and code for our paper (in french):

@@

You can download the compendium as a zip from from this [URL](http://github.com/nfrerebeau/archeosciences2019/archive/master.zip).

Or you can install this compendium as an R package, `archeosciences2019`, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("nfrerebeau/archeosciences2019")
```

@@

* The Rmarkdown source file of the manuscript (in the `paper/` subdirectory),
* All the figures generated from R code (in the `figures/` subdirectory),
* All the raw data files (in CSV format, in the `data/` subdirectory),
* Code files used for data cleaning (in the `scripts/` subdirectory).
